### 2025-09-18 paper/sec/evaluation.tex
Corrections to Table 2.
Minor corrections.

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{p{3cm} p{6cm} p{4cm}}
        \hline
        \textbf{Ambiguity Type} & \textbf{Example} & \textbf{Explanation} \\
        \hline

@@

        missing-data &
        The average methane emissions for the year 2015 is \hl{1.0} &
        November is missing to calculate the average correctly. \\

@@

        \hline
    \end{tabular}
    \caption{Negative cases example without the \emph{Data} column.}
    \label{tab:ambiguita}
\end{table}

>>>>

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{l p{6cm} p{4cm}}
        \hline
        \textbf{Problem Type} & \textbf{Example} & \textbf{Explanation} \\
        \hline

@@

        missing data &
        The average methane emissions for the year 2015 is \hl{1.0} &
        November is missing to calculate the average correctly. \\

@@

        \hline
    \end{tabular}
    \caption{Categories of problematic example}
    \label{tab:ambiguita}
\end{table}
